---
title: "Week7New"
author: "Banu Boopalan"
date: "10/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Install Downloader
library(downloader)
library(stringr)
#Install Reshape pacakge 
#Start building data needed to calculate final average prechess rating
library(reshape)
library(tibble)
library(dplyr)
library(knitr)
#Install KableExtra package and use that
library(kableExtra)
library(dplyr)
library(rvest)
library("XML")
library("methods")
library(RCurl)
library(RJSONIO)
```

## I created my file for html manually and reading it in as an HTML file.


```{r}
myurl <- "https://raw.githubusercontent.com/BanuB/Week7Assignment/master/Books2.html"
html<-tbl_df(as.data.frame(read_html(myurl) %>% html_table(header = NA, trim=TRUE, fill=TRUE)))
html %>% kable() %>% kable_styling() %>% scroll_box(width = "910px")
```

## Created and read in an XML file



```{r}
myXML <- getURL("https://raw.githubusercontent.com/BanuB/Week7Assignment/master/BooksXML2.xml")
xmlData<-xmlToDataFrame(myXML)
xmlData %>% kable() %>% kable_styling() %>% scroll_box(width = "910px")
```

## Reading in a json file



```{r}
myjson<-fromJSON(content = "https://raw.githubusercontent.com/BanuB/Week7Assignment/master/Booksjson.JSON")
myjsontb<-do.call("cbind", lapply(myjson[[1]], data.frame, stringsAsFactors = FALSE))
s <- t(myjsontb)
s %>% kable() %>% kable_styling() %>% scroll_box(width = "910px")

str(xmlData)
str(html)
str(s)

```

## 
For the HTML file creation, I manually created the file, For XML, manually created a file as well. For XML the & in the attribute value caused an error so I had to resubmit the equivalent &amp; . JSON file was created but I had to use like lapply and transpose steps to show the information in a dataframe format. The HTML and XML seem to similar in structure. For JSON, we were reading in a list and then I  perform cbind and then transpose to get it in the similar structure as the HTML and XML files.